%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%% Copyright (c) 2023 Hunter Figgs
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[calibri]{my-resume}

% For mathematical symbols
\usepackage{amsmath}

% For hyperlinks
\usepackage{hyperref}
\hypersetup{
	pdftitle={Hunter Figgs Resume}
	}

% For line spacing
\usepackage{setspace}
\setstretch{1.05}

% Set applicant's personal data for header
\name{Hunter Figgs}
\address{Address \linebreak City State Zip}
\contacts{(XXX) XXX-XXXX \linebreak hunter.figgs@gmail.com}

\begin{document}

	% Print the header
	\makeheader

	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Robotics Software Engineer}{ThorDrive}{July 2022 -- March 2023}
			\begin{itemize}
				\item LiDAR Sensor Grabber
				\begin{itemize}
					\item Reduced computation load by 60\% after profiling software module with Valgrind Callgrind and eliminating recurring memory allocations with RAII
					\item Improved data latency by 3 milliseconds by refactoring code to use ROS zero-copy transfer
					\item Rewrote networking code to utilize Boost.ASIO to make code robust and maintainable
				\end{itemize}
				\item Flight Trajectory Prediction
				\begin{itemize}
					\item Developed real-time airplane trajectory prediction module to assist with autonomous vehicle navigation
					\item Implemented motion model to reliably predict short-term airplane movements
				\end{itemize}
				\item Sensor Calibration
				\begin{itemize}
					\item Adapted open-source calibration software into robot production to save days of manual labor
				\end{itemize}
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer Intern}{ThorDrive}{May 2021 -- Dec. 2021}
			\begin{itemize}
				\item Vehicle Control \& Diagnostic GUI
				\begin{itemize}
					\item Developed Python GUI application for vehicles to improve user experience/efficiency
					\item Integrated with ROS to send vehicle commands, report diagnostics (GPS fix, battery health, etc.), log data
				\end{itemize}
				\item Flight Data Grabber
				\begin{itemize}
					\item Created module to capture and process real-time flight data to aid vehicle perception
				\end{itemize}
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{DevOps/TestOps Intern}{Siemens Healthineers}{May 2020 -- Aug. 2020}
			\begin{itemize}
				\item Server Usage Dashboard
				\begin{itemize}
					\item Built web dashboard to report statistics on MS Azure build server utilization
					\item Reports were used to make decision on \$500,000 purchase of server equipment
				\end{itemize}
				\item Chosen for Intern Spotlight of the Week
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Teaching Assistant}{Engineering Dept. Ohio State}{Aug. 2019 -- Dec. 2019}
			\begin{itemize}
				\item Taught advanced programming section of Honors Fundamentals of Engineering course
				\begin{itemize}
					\item Topics: technical writing, eng. design process, eng. ethics, C/C++, MATLAB
				\end{itemize}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Columbus, OH}{Ohio State University}{Aug. 2018 -- May 2022}
			\begin{itemize}
				\item B.S. in Computer Science \& Engineering, May 2022, GPA: 3.9
				\begin{itemize}
					\item Coursework: Algorithms; Operating Systems; Databases; Networking; Neural Networks; Computer Vision; Speech and Language Processing; Advanced Artificial Intelligence
				\end{itemize}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{\href[pdfnewwindow=true]{https://github.com/hfiggs/hunterfiggs.com}{hunterfiggs.com}} Personal website to showcase projects. JavaScript, CSS, HTML
				\item \textbf{\href[pdfnewwindow=true]{https://www.hunterfiggs.com/projects/detect-digit}{Detect Digit}} (Present) A handwritten digit detector, using computer vision and machine learning techniques.
				\begin{itemize}
					\item Implemented FastAPI Python server to handle detection requests; Trained KNN model on MNIST dataset
					\item Created CI/CD pipeline to run unit/integration tests, build Docker image, and deploy to GCP Cloud Run
				\end{itemize}
				\item \textbf{\href[pdfnewwindow=true]{https://www.hunterfiggs.com/projects/zelda-clone/zelda-clone.html}{NES Zelda Clone}} (Autumn 2020). Collaborative school project to recreate classic video game. C\#.NET
				\begin{itemize}
					\item Implemented A* enemy search, collision detection, and ray-casting lighting system
				\end{itemize}
				\item \textbf{HackOHI/O Hackathon} (2019). 24-hour, top-down shooter in the browser. JavaScript, p5.js, HTML
				\item \textbf{Robotics Competition} (Spring 2019). Collaborative school project to design robot to navigate course and complete objectives. Implemented PID control system. Placed top 16 out of 100 teams. C++, SolidWorks
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item C++; Python; C\#.NET; Java, JavaScript/HTML/CSS; PowerShell; SQL
				\item Docker; GCP; Boost; ROS; CMake; Visual Studio; Valgrind Callgrind; Kivy; SolidWorks
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

\end{document}
